---
title: "Case 11"
author: "Suiyuan Wang"
date: "11/15/2022"
output: 
    html_document:
    toc: true
    toc_depth: 2
always_allow_html: true
knit: {rmarkdown::render("case_study_11.Rmd",output_format = "all")}
---

```{r setup, include=FALSE}
library(tidyverse)
library(spData)
library(sf)

## New Packages
library(mapview) # new package that makes easy leaflet maps
library(foreach)
library(doParallel)
registerDoParallel(4)
getDoParWorkers() # check registered cores
```


```{r}
# go to  http://api.census.gov/data/key_signup.html and get a key, then run the line below with your key.  Don't push your key to github!
library(tidycensus)
#census_api_key("83e6682de7bfa24b9c6133fc65a0aea557d1f7b4")
```

```{r}
library(tidycensus)
racevars <- c(White = "P005003", 
              Black = "P005004", 
              Asian = "P005006", 
              Hispanic = "P004003")

options(tigris_use_cache = TRUE)
erie <- get_decennial(geography = "block", variables = racevars, 
                  state = "NY", county = "Erie County", geometry = TRUE,
                  summary_var = "P001001", cache_table=T) 
```

Crop the county-level data to `c(xmin=-78.9,xmax=-78.85,ymin=42.888,ymax=42.92)` to reduce the computational burdern. Feel free to enlarge this area if your computer is fast (or you are patient).

```{r}
buffalo <- st_crop(erie, c(xmin=-78.9,xmax=-78.85,ymin=42.888,ymax=42.92))

buffalo$variable = as.factor(buffalo$variable)
variable_vec = as.array(unique(buffalo$variable))
```
Write a foreach loop that does the following steps for each racial group in the variable column of the erie dataset and rbinds the results (e.g. .combine=rbind) into a single sf object. You may want to convert the variable column into a factor and use levels() or use unique().
filter the the data to include only one race at time
use st_sample() to generate random points for each person that resided within each polygon. If you use a pipe (%>%), you will have to set size=.$value. The . indicates that the column comes from the dataset that was passed to the function. See here for details on how to use the . in a pipe.
convert the points from st_sample() to spatial features with st_as_sf()
mutate to add a column named variable that is set to the current racial group (from the foreach loop)
```{r}
race_points <- foreach(i=1:4,.combine=rbind) %dopar%{
  buffalo %>% 
  filter(variable==unique(buffalo$variable)[i]) %>%
  st_sample(size=.$value) %>% 
  st_as_sf() %>%
  mutate(variable = unique(buffalo$variable)[i])
  }

mapview(race_points, zcol='variable', cex=1, alpha=0)
```
