---
title: "case_study_12"
author: "Suiyuan Wang"
date: "12/5/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggmap)
library(htmlwidgets)
library(widgetframe)
library(tidyverse)
library(rnoaa)
library(xts)
library(doParallel)
library(dygraphs)
```


```{r}
d=meteo_tidy_ghcnd("USW00014733",
                   date_min = "2016-01-01", 
                   var = c("TMAX"),
                   keep_flags=T) %>% 
   mutate(date=as.Date(date),
          tmax=as.numeric(tmax)/10) 
d_xts=xts(d$tmax,order.by=d$date)
```

Remaining steps:

Convert d into an xts time series object using xts(). You will need to specifify which column has the data (d$tmax) and order.by=d$date. See ?xts for help.
1. Use dygraph() to draw the plot
2. Set the title of the dygraph to be main="Daily Maximum Temperature in Buffalo, NY"
3. Add a dyRangeSelector() with a dateWindow of c("2020-01-01", "2020-10-31")
4. Explore other options. You could download another variable (precipitation?) and add it to the plot. Or imagine another way to visualize the data using one of the other interactive libraries.

```{r}
plot = dygraph(d_xts, main = 'Daily Maximum Temperature in Buffalo, NY')

dyRangeSelector(plot, dateWindow = c("2020-01-01", "2020-10-31"))
```