---
title: "Case_06"
author: "Suiyuan Wang"
date: "10/11/2022"
output: 
    github_document: default
    theme: blank
    highlight: blank
---
# Find hottest country on each continent 
## --Use mean temperature for each country
Load packages
```{r include = FALSE}
library(raster)
library(sp)
library(spData)
library(tidyverse)
library(sf)
library(knitr)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Datasets used in this study.
### Load 'world' data from spData package
```{r}
data(world)
```
### Get long term mean temperature data from the Climatic Research Unit (CRU).
```{r}
library(ncdf4)
download.file("https://crudata.uea.ac.uk/cru/data/temperature/absolute.nc","crudata.nc")
tmean=raster("crudata.nc")
```
##1. Prepare country polygon data (the `world` object).
### 1) Remove “Antarctica” with `filter()` because WorldClim does not have data there.
```{r}
world_remove_Antarctica <- world %>%
  filter(continent != "Antarctica")
```
### 2) Convert the `world` object to `sp` format (the ‘old’ format) because the `raster` package doesn’t accept `sf` objects. you can do this with `as(world,"Spatial")`.
```{r}
world_remove_Antarctica_sp <- as(world_remove_Antarctica,"Spatial")
```
## 2. Prepare Climate Data
### 1) Get long term mean temperature data from the Climatic Research Unit (CRU) ---`tmean` in above codes.
### 2) Inspect the new tmean object (you can start by just typing it’s name `tmean`, then perhaps making a `plot()`). How many layers does it have? What do these represent? You can read more about the data [here](https://www.worldclim.org/data/worldclim21.html).
```{r}
tmean
plot(tmean)
```

### 3) The WorldClim data are stored as hundreths of degrees C. So a real value of 15.5 C would be stored as 155. This saves disk space because they can be stored as `integers` instead of `floating point` numbers. This means each value needs to be multiplied by `0.1` to convert back to degrees C. You can do this with `gain()`.
```{r}
gain(tmean) <- gain(tmean)
plot(tmean)
```

### 4) Create a new object called `tmax_annual` that is the annual maximum temperature in each pixel of the raster stack using `max()`. This will find the maximum temperature in each location across all months.
```{r}
tmax_annual <- max(tmean)
plot(tmax_annual)
tmax_annual
```

### 5) Use `names(tmax_annual) <- "tmax"` to change the name of the layer in the new tmax_annual object to tmax. This makes the later code more intuitive than keeping the default name layer.
```{r}
names(tmax_annual) <- "tmax"
```
## 3. Calculate the **maximum mean temperature** observed in each country.
### 1) use `raster::extract()` to identify the maximum temperature observed in each country (`fun=max`). Also set `na.rm=T, small=T, sp=T` to 1) handle missing data along coastlines, 2) account for small countries that may not have a full 0.5 degree pixel in them, and 3) return a spatial polygon object instead of just a vector of values.
```{r}
tmax_annual_1 <- raster::extract(x = tmax_annual, y = world_remove_Antarctica_sp, fun = max, na.rm =T, small = T, sp = T)
```

### 2) convert the results of the previous step to sf format with `st_as_sf()`. Now you have an updated polygon object with a new column of maximium temperature. Cool!
### 3) save this spatial feature as `tmax_country`.
```{r}
tmax_country <- st_as_sf(tmax_annual_1)
```
## 4. Communicate your results
### 1) use `ggplot()` and `geom_sf()` to plot the maximum temperature in each country polygon (not the original raster layer). To recreate the image below, you will also need `+scale_fill_viridis_c(name="Annual\nMaximum\nTemperature (C)")`. Note the use of `\n` to insert a line break in the text string. You can move the legend around with `+theme(legend.position = 'bottom')`.
```{r}
ggplot(tmax_country) + 
  geom_sf(aes(fill = tmax)) +
  coord_sf(label_graticule = "SW", label_axes = "SW") +
  scale_fill_viridis_c(name="Annual\nMaximum\nTemperature (°C)") +
  theme(legend.position = 'bottom')
```

### 2) use dplyr tools to find the hottest country in each continent. You may need group_by() and top_n. To create a nice looking table, you may also want to use select() to keep only the desired columns, arrange() to sort them, st_set_geometry(NULL) to drop the geometry column (if desired). Save this table as hottest_continents.
```{r}
hottest_countries <- tmax_country %>%
  group_by(continent) %>%
  select(name_long, continent, tmax) %>%
  arrange(desc(tmax)) %>%
  st_set_geometry(NULL) %>%
  top_n(1,tmax)

kable(hottest_countries)
```